---
title: "P8105_hw3_cx2257"
author: "Congyang Xie"
date: "10/17/2021"
output: github_document
---
```{r, echo=FALSE, message=FALSE}
library(tidyverse)

```

## Problem 1

```{r}
library(p8105.datasets)
data("instacart")
```
1. **Description of the dataset**: The instacart dataset contains `r nrow(instacart)` observations and `r ncol(instacart)` variables. The varibales are `r names(instacart)`. The dataset inclueds `r length(unique(pull(instacart, product_name)))` different products, which belongs to `r length(unique(pull(instacart, aisle)))` aisles in `r length(unique(pull(instacart, department)))` departments. The dataset records how products get added into different shopping carts by different users and the products' information as well. For example, `r pull(instacart, product_name)[1]` was added to the order `r pull(instacart, order_id)[1]` by customer whose user id is `r pull(instacart, user_id)[1]` at `r pull(instacart, order_hour_of_day)[1]` o'clock, which is the `r pull(instacart, add_to_cart_order)[1]`st product added to the cart.

2. **How many aisles are there, and which aisles are the most items ordered from?**

  There are `r length(unique(pull(instacart, aisle)))` aisles. The top 3 aisles that are frequently ordered from are stated below:
  
```{r}
instacart %>% 
  count(aisle) %>%
  arrange(desc(n)) %>%
  head(3) %>%
  knitr::kable()
```
 
3. **Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.**
  
```{r}
instacart %>%
  count(aisle) %>%
  filter(n > 10000) %>%
  arrange(desc(n)) %>%
  mutate(aisle = factor(aisle, levels = aisle)) %>%
  ggplot(aes(x = aisle, y = n)) +
  geom_segment(aes(xend = aisle, yend = 1), width = 15) +
  geom_point(size = 4, color = "pink") +
  coord_flip() +
  theme_bw() +
  xlab("")
```



 

