---
title: "P8105_hw3_cx2257"
author: "Congyang Xie"
date: "10/17/2021"
output: github_document
---
```{r, echo=FALSE, message=FALSE}
library(tidyverse)

```

## Problem 1

```{r}
library(p8105.datasets)
force(data("instacart"))
```
1. **Description of the dataset**: The instacart dataset contains `r nrow(instacart)` observations and `r ncol(instacart)` variables. The varibales are `r names(instacart)`. The dataset inclueds `r length(unique(pull(instacart, product_name)))` different products, which belongs to `r length(unique(pull(instacart, aisle)))` aisles in `r length(unique(pull(instacart, department)))` departments. The dataset records how products get added into different shopping carts by different users and the products' information as well. For example, `r pull(instacart, product_name)[1]` was added to the order `r pull(instacart, order_id)[1]` by customer whose user id is `r pull(instacart, user_id)[1]` at `r pull(instacart, order_hour_of_day)[1]` o'clock, which is the `r pull(instacart, add_to_cart_order)[1]`st product added to the cart.

2. **How many aisles are there, and which aisles are the most items ordered from?**

  There are `r length(unique(pull(instacart, aisle)))` aisles. The top 3 aisles that are frequently ordered from are stated below:
  
```{r}
instacart %>% 
  count(aisle) %>%
  arrange(desc(n)) %>%
  head(3) %>%
  knitr::kable()
```
 
3. **Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.**
  
```{r}
instacart %>%
  count(aisle) %>%
  filter(n > 10000) %>%
  arrange(desc(n)) %>%
  mutate(aisle = factor(aisle, levels = aisle)) %>%
  ggplot(aes(x = aisle, y = n)) +
  geom_segment(aes(xend = aisle, yend = 1)) +
  geom_point(size = 4, color = "pink") +
  coord_flip() +
  theme_bw() +
  xlab("")
```

4. **Make a table showing the three most popular items in each of the aisles "baking ingredients", "dog food care", and "packaged vegetables fruits". Include the number of times each item is ordered in your table.**

```{r}
freq_prod <- instacart %>%
  filter(aisle == c(
    "baking ingredients",
    "dog food care",
    "packaged vegetables fruits"
  )) %>%
  select(aisle, product_name) %>%
  group_by(aisle) %>%
  count(product_name, sort = TRUE) %>%
  top_n(n = 3, wt = product_name) %>%
  arrange(aisle, desc(n))

freq_prod %>% knitr::kable() 
```

5. **Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).**

```{r warning=FALSE}
order_mean_hour_df <- 
  instacart %>%
  select(product_name, order_dow, order_hour_of_day) %>%
  filter(product_name == c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>%
  mutate(order_mean_hour = mean(order_hour_of_day)) %>%
  arrange(product_name, order_dow) %>%
  select(-order_hour_of_day) %>%
  distinct() %>%
  pivot_wider(names_from = order_dow, values_from = order_mean_hour)
  

names(order_mean_hour_df)[2:8] <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
order_mean_hour_df %>% knitr::kable(caption = "The mean hour of items ordered each weekday")


```
 
## Problem 2

```{r}
# load data
force(data("brfss_smart2010"))
```


```{r}
# clean and tidy data

brfss_df <-
  brfss_smart2010 %>%
  janitor::clean_names() %>%
  filter(topic == "Overall Health") %>%
  mutate(response = factor(
    response,
    levels = c("Poor", "Fair", "Good", "Very good", "Excellent")
  ))

```

