---
title: "P8105_hw3_cx2257"
author: "Congyang Xie"
date: "10/17/2021"
output: github_document
---
```{r, echo=FALSE, message=FALSE}
library(tidyverse)
library(patchwork)
```

## Problem 1

```{r}
library(p8105.datasets)
force(data("instacart"))
```
1. **Description of the dataset**: The instacart dataset contains `r nrow(instacart)` observations and `r ncol(instacart)` variables. The varibales are `r names(instacart)`. The dataset inclueds `r length(unique(pull(instacart, product_name)))` different products, which belongs to `r length(unique(pull(instacart, aisle)))` aisles in `r length(unique(pull(instacart, department)))` departments. The dataset records how products get added into different shopping carts by different users and the products' information as well. For example, `r pull(instacart, product_name)[1]` was added to the order `r pull(instacart, order_id)[1]` by customer whose user id is `r pull(instacart, user_id)[1]` at `r pull(instacart, order_hour_of_day)[1]` o'clock, which is the `r pull(instacart, add_to_cart_order)[1]`st product added to the cart.

2. **How many aisles are there, and which aisles are the most items ordered from?**

  There are `r length(unique(pull(instacart, aisle)))` aisles. The top 3 aisles that are frequently ordered from are stated below:
  
```{r}
instacart %>% 
  count(aisle) %>%
  arrange(desc(n)) %>%
  head(3) %>%
  knitr::kable()
```
 
3. **Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. Arrange aisles sensibly, and organize your plot so others can read it.**
  
```{r fig.height=6, fig.width=8}
instacart %>%
  count(aisle) %>%
  filter(n > 10000) %>%
  arrange(desc(n)) %>%
  mutate(aisle = factor(aisle, levels = aisle)) %>%
  ggplot(aes(x = aisle, y = n)) +
  geom_segment(aes(xend = aisle, yend = 1), color = "#B1B479") +
  geom_point(size = 4, color = "pink") +
  coord_flip() +
  theme_bw() +
  xlab("")
```

4. **Make a table showing the three most popular items in each of the aisles "baking ingredients", "dog food care", and "packaged vegetables fruits". Include the number of times each item is ordered in your table.**

```{r}
freq_prod <- instacart %>%
  filter(aisle == c(
    "baking ingredients",
    "dog food care",
    "packaged vegetables fruits"
  )) %>%
  select(aisle, product_name) %>%
  group_by(aisle) %>%
  count(product_name, sort = TRUE) %>%
  top_n(n = 3, wt = product_name) %>%
  arrange(aisle, desc(n))

freq_prod %>% knitr::kable() 
```

5. **Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).**

```{r warning=FALSE}
order_mean_hour_df <- 
  instacart %>%
  select(product_name, order_dow, order_hour_of_day) %>%
  filter(product_name == c("Pink Lady Apples", "Coffee Ice Cream")) %>%
  group_by(product_name, order_dow) %>%
  mutate(order_mean_hour = mean(order_hour_of_day)) %>%
  arrange(product_name, order_dow) %>%
  select(-order_hour_of_day) %>%
  distinct() %>%
  pivot_wider(names_from = order_dow, values_from = order_mean_hour)
  

names(order_mean_hour_df)[2:8] <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
order_mean_hour_df %>% knitr::kable(caption = "The mean hour of items ordered each weekday", digits = 2)


```
 
## Problem 2

```{r}
# load data
force(data("brfss_smart2010"))
```


```{r}
# clean and tidy data

brfss_df <-
  brfss_smart2010 %>%
  janitor::clean_names() %>%
  filter(topic == "Overall Health") %>%
  mutate(response = factor(
    response,
    levels = c("Poor", "Fair", "Good", "Very good", "Excellent")
  ))

```

1. In 2002, which states were observed at 7 or more locations? What about in 2010?

In 2002, states that were obeserved at least 7 locations are stated below:
```{r}
brfss_df %>%
  select(year, locationabbr, locationdesc) %>%
  filter(year == 2002) %>%
  group_by(locationabbr) %>%
  summarise(n_obs = n_distinct(locationdesc)) %>%
  filter(n_obs > 6) %>%
  arrange(desc(n_obs)) %>%
  knitr::kable(caption = "states that were obeserved at least 7 locations in 2002")
```

In 2010, states that were obeserved at least 7 locations are stated below:

```{r}
brfss_df %>%
  select(year, locationabbr, locationdesc) %>%
  filter(year == 2010) %>%
  group_by(locationabbr) %>%
  summarise(n_obs = n_distinct(locationdesc)) %>%
  filter(n_obs > 6) %>%
  arrange(desc(n_obs)) %>%
  knitr::kable(caption = "states that were obeserved at least 7 locations in 2010")
```

2. Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state. Make a “spaghetti” plot of this average value over time within a state (that is, make a plot showing a line for each state across years – the geom_line geometry and group aesthetic will help).

```{r}
excellent_df <- 
  brfss_df %>%
  filter(response == "Excellent") %>%
  group_by(locationabbr, year) %>%
  summarise(avg_data_value = mean(data_value, na.rm = TRUE)) 
```
```{r fig.height=5, fig.width=10}
excellent_df %>%
  ggplot(aes(x = year, y = avg_data_value)) +
  geom_line(aes(group = locationabbr, color = locationabbr)) +
  viridis::scale_color_viridis(discrete = T) +
  theme_bw()
```

3. Make a two-panel plot showing, for the years 2006, and 2010, distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State.

```{r echo=TRUE, fig.height=8, fig.width=10, message=FALSE, warning=FALSE, paged.print=FALSE}
data_value_06 <-
  brfss_df %>%
  filter(year == 2006, 
         response == "Poor" | response == "Excellent",
         locationabbr == "NY") %>%
  ggplot(aes(x = locationdesc, y = data_value, fill = response)) +
  geom_bar(position = "dodge", stat = "identity") +
  viridis::scale_fill_viridis(discrete = TRUE) +
  ggtitle("data_value distribution in 2006") +
  theme_bw()

data_value_10 <-
  brfss_df %>%
  filter(year == 2010, 
         response == "Poor" | response == "Excellent",
         locationabbr == "NY") %>%
  ggplot(aes(x = locationdesc, y = data_value, fill = response)) +
  geom_bar(position = "dodge", stat = "identity") +
  viridis::scale_fill_viridis(discrete = TRUE) +
  ggtitle("data_value distribution in 2010") +
  theme_bw()

data_value_06 / data_value_10


```

## Problem 3

1. Load, tidy, and otherwise wrangle the data. Your final dataset should include all originally observed variables and values; have useful variable names; include a weekday vs weekend variable; and encode data with reasonable variable classes. Describe the resulting dataset (e.g. what variables exist, how many observations, etc).

```{r message=FALSE, warning=FALSE}
accel_data_df <- read_csv("accel_data.csv") %>%
  janitor::clean_names() %>%
  pivot_longer(
    activity_1:activity_1440,
    names_to = "act_minute",
    names_prefix = "activity_",
    values_to = "activity_counts"
  ) %>%
  mutate(
    weekday_or_weekend = if_else(day %in% c("Saturday", "Sunday"), "Weekend", "Weekday"),
    day = forcats::fct_relevel(day, c("Monday", "Tuesday", "Wednesday", 
                              "Thursday", "Friday", "Saturday", "Sunday"))
  ) 
```
**Description of the dataset**: The instacart dataset contains `r nrow(accel_data_df)` observations and `r ncol(accel_data_df)` variables. The varibales are `r names(accel_data_df)`.

2. Traditional analyses of accelerometer data focus on the total activity over the day. Using your tidied dataset, aggregate accross minutes to create a total activity variable for each day, and create a table showing these totals. Are any trends apparent?

```{r}
minute_activity_df <-
accel_data_df %>%
  group_by(week, day) %>%
  summarise(total_counts = sum(activity_counts)) %>%
  pivot_wider(names_from = week, values_from = total_counts, names_prefix = "week_")

knitr::kable(minute_activity_df, digits = 2)
```
There is no apparent trend here. It seems that the patient took some rest on the saturday of week4 and week5.

3. Accelerometer data allows the inspection activity over the course of the day. Make a single-panel plot that shows the 24-hour activity time courses for each day and use color to indicate day of the week. Describe in words any patterns or conclusions you can make based on this graph.

```{r fig.height=6, fig.width=10}
hour_activity_df <-
accel_data_df %>% 
  mutate(act_hour = floor((as.numeric(act_minute)-1)/60)) %>%
  group_by(day, act_hour) %>%
  summarise(hour_sum = sum(activity_counts))

hour_activity_df %>% 
  ggplot(aes(x = act_hour, y = hour_sum)) +
  geom_line(aes(group = day, color = day)) +
  viridis::scale_fill_viridis(discrete = TRUE) +
  ggtitle("24-hr activity sum for each day") +
  theme_bw()
```
The patient has 2 peak activity periods at a day, one is around 11, 12 o'clock at noon, another is around 8 o'clock at night. The patient's activity sharply went down after going to sleep and stayed at a very low level until waking up in the morning.
