---
title: "P8105_hw3_cx2257"
author: "Congyang Xie"
date: "10/17/2021"
output: github_document
---
```{r, echo=FALSE, message=FALSE}
library(tidyverse)
```

## Problem 1

```{r}
library(p8105.datasets)
data("instacart")
```
1. **Description of the dataset**: The instacart dataset contains `r nrow(instacart)` observations and `r ncol(instacart)` variables. The varibales are `r names(instacart)`. The dataset inclueds `r length(unique(pull(instacart, product_name)))` different products, which belongs to `r length(unique(pull(instacart, aisle)))` aisles in `r length(unique(pull(instacart, department)))` departments. The dataset records how products get added into different shopping carts by different users and the products' information as well. For example, `r pull(instacart, product_name)[1]` was added to the order `r pull(instacart, order_id)[1]` by customer whose user id is `r pull(instacart, user_id)[1]` at `r pull(instacart, order_hour_of_day)[1]` o'clock, which is the `r pull(instacart, add_to_cart_order)[1]`st product added to the cart.

2. 


 

